
\subsection{MonitoringNode}
Main Class wrapping the processing functionality.

\subsubsection{Attributes}
\begin{itemize}
	\item private MetadataStorage storage
	\item private SpecificationHandler specHandler
\end{itemize}
\subsubsection{Methods}
\begin{itemize}
	\item \textbf{private Metadata receive\_data()}\\
	Receives data incoming from the Subscriber and converts them to Metadata objects.
	\item \textbf{private ComparisonResult process\_data(Metadata)}\\
	Returns the specHandler's compare result
	\item \textbf{private void publish\_data(ComparisonResult)}\\
	Publishes results of the comparison as rated Metadata
	\item \textbf{private MetadataStorageResponse storage\_server(MetadataStorageRequest)}\\
	Listen for the GUI Model service calls and returns requested metadata from the storage
\end{itemize}


\subsection{MetadataStorage}
Saves recieved metadata packages for a given period of time and can provide them on request.

\subsubsection{Attributes}
\begin{itemize}
	\item \textbf{private dict(string, dict(int, StorageContainer[])) storage}\\
	Datastructure to store Packages by key and timestamp
	\item \textbf{private int duration}\\
	Duration in seconds for data to be stored
\end{itemize}
\subsubsection{Methods}
\begin{itemize}
	\item \textbf{private void clean\_up()}\\
	Deletes Metadata exceeding the duration to store
	\item \textbf{public boolean store(StorageContainer)}\\
	Stores a given Metadata
	\item \textbf{public StorageContainer[] get(string, int)}\\
	Returns all Metadata packages for the given connection/host of the given amount of time.
	\item \textbf{public boolean clear()}\\
	Clears the whole storage
\end{itemize}


\subsection{StorageContainer}
Wraps Metadata in raw and rated form with an identifier and a timestamp. Object to be returned on request by the GUI model.

\subsubsection{Attributes}
\begin{itemize}
	\item \textbf{public int timestamp}\\
	Time when the data came from the subscriber
	\item \textbf{public string identifier}\\
	Host/Node/Connection identifier
	\item \textbf{public object data\_raw}\\
	The data as it reaches the subscriber from nodes and hosts.
	\item \textbf{public object data\_rated}\\
	The data like it would be published after being rated.
\end{itemize}


\subsection{Metadata}
Wraps metadata of exactly one host or node, a topic or a node-topic-combination.

\subsubsection{Attributes}
\begin{itemize}
	\item \textbf{private MetadataTuple[] values}\\
	Collection of Metadata regarding multiple meassurements.
\end{itemize}
\subsubsection{Methods}
\begin{itemize}
	\item \textbf{public void add\_tuple(MetadataTuple)}\\
	Add a MetadataTuple of information to the bundle.
	\item \textbf{public object get(String)}\\
	Returns the value of the MetadataTuple with the given key. False, if the key does not exist.
\end{itemize}


\subsection{Specification}
An object loaded from the specification configurations and basis for comparison of Metadata with desired values.

\subsubsection{Attributes}
\begin{itemize}
	\item \textbf{private MetadataTuple[] values}\\
	Collection of MetadataTuple objects providing limits for multiple fields.
\end{itemize}
\subsubsection{Methods}
\begin{itemize}
	\item \textbf{public void add\_tuple(MetadataTuple)}\\
	Adds a MetadataTuple to the bundle
	\item \textbf{public Object get(String)}\\
	Returns the value of the MetadataTuple with the given key. The returned value would be a list containing limit values for the most measured fields. False, if the key does not exist.
\end{itemize}


\subsection{SpecificationHandler}
Loads the specifications from the parameter server and compares them to the actual metadata.

\subsubsection{Attributes}
\begin{itemize}
	\item \textbf{private Specification[] specifications}\\
	Datastructure to keep all loaded Specification objects
\end{itemize}
\subsubsection{Methods}
\begin{itemize}
	\item \textbf{private void load\_specifications()}\\
	Loads the specifications from configuration files into Specification objects and stores them
	\item \textbf{public RatedStatistics compare(Metadata, Specification)}\\
	Compares a given Metadata object with a given Specification object regarding all available fields. Returns a RatedStatistics object wrapping potential divergences.
\end{itemize}


\subsection{RatedStatistics}
Wraps the result of the comparison between the actual metadata and the specificaton.

\subsubsection{Attributes}
\begin{itemize}
	\item \textbf{public string seuid}\\
	Identifies the node/host/connection
	\item \textbf{public string[] metatype}\\
	The metadata that was out of bounds
	\item \textbf{public string[] actual}\\
	The actual values
	\item \textbf{public string[] expected}\\
	The expected values
	\item \textbf{public int[] state}\\
	State of the metadata from the node/host/connection : state: { 0 = high ; 1 = low ; 2 = unknown}
\end{itemize}


\subsection{MetadataTuple}
Stores any kind of value for a certain key. Specifications storing values indicating limits, Metadata storing absolute actual values.

\subsubsection{Attributes}
\begin{itemize}
	\item private String key
	\item private Object value
\end{itemize}
\subsubsection{Methods}
\begin{itemize}
	\item public String get\_key()
	\item public Object get\_value()
\end{itemize}